---
title: "Calciphylaxis - preliminary analyses"
author: "Huckle / Ritchie / Sinha"
output: pdf_document
---
```{r, echo=FALSE, print=FALSE, include=FALSE}
#REPRODUCE THE DATA CLEANING

#SET WORKING DIRECTORY
setwd("~/Dropbox/Calciphylaxis")

#DEFINE PACKAGES
require(readxl)
require(dplyr)
require(tidyr)
require(ggplot2)

#IMPORT DATA
  CAL_baseline<-read_excel("Calciphylaxis.xlsx",sheet=1)
  CAL_followup<-read_excel("Calciphylaxis.xlsx",sheet=2)
  
  CAL_baseline_unedited<-read_excel("Calciphylaxis.xlsx",sheet=1)

##### FIRST CLEAN BASELINE DATA SHEET  
  
#ASSIGN DATA CHARACTERISITCS / LABEL CORRECTLY
  #baseline
  CAL_baseline$LocalContactEmail<-NULL #Not useful to analysis
  CAL_baseline$Date<-NULL #missing data and appears largely to duplicate consent date column
  CAL_baseline$`1_Consent`<-NULL #Not useful to analysis
  CAL_baseline$`1a_ConsentDate`<-as.Date(CAL_baseline$`1a_ConsentDate`, "%d/%m/%Y")
  CAL_baseline$`1b_Gender`<-ifelse(CAL_baseline$`1b_Gender`=="1","Male",ifelse(CAL_baseline$`1b_Gender`=="2", "Female", NA))
  CAL_baseline$`1d_Weight`<-NULL #38/71 missing
  CAL_baseline$`1e_BMI`<-NULL #39/71 missing
  CAL_baseline$`2_Race`<-NULL #Awaiting key from Abby; only 4 are not coded as '1' so likely uninformative for analysis
  CAL_baseline$`3_DateFirstTreatment`<-as.Date(CAL_baseline$`3_DateFirstTreatment`, "%d/%m/%Y") #For analysis, presume this is first HD - need to confirm with Abby
  #Column 5_ not yet addressed as need to understand the coding
  CAL_baseline$`4_RenalStatus`<-ifelse(CAL_baseline$`4_RenalStatus`=="1", "CKD1", 
                                ifelse(CAL_baseline$`4_RenalStatus`=="2", "CKD2", 
                                ifelse(CAL_baseline$`4_RenalStatus`=="3", "CKD3a", 
                                ifelse(CAL_baseline$`4_RenalStatus`=="4", "CKD3b", 
                                ifelse(CAL_baseline$`4_RenalStatus`=="5", "CKD4", 
                                ifelse(CAL_baseline$`4_RenalStatus`=="6", "CKD5", 
                                ifelse(CAL_baseline$`4_RenalStatus`=="7", "Transplant", 
                                ifelse(CAL_baseline$`4_RenalStatus`=="8", "HD/HDF", 
                                ifelse(CAL_baseline$`4_RenalStatus`=="9", "PD", 
                                ifelse(CAL_baseline$`4_RenalStatus`=="10", "Non-CKD", NA))))))))))
  
  #Update binary co-morbidities to Yes / No for clarity of reading (columns 5 / 6)
  #function
  Comorbid_code<- function(x) {
                     x<-as.character(x)
                     x<-ifelse(x == "1", "Yes",ifelse(x =="2","No",  NA)) #<<- to return to global environment
                     x<<-as.factor(x)
  }
  
  #lapply over appropraite columns
  CAL_baseline[7:9]<-lapply(CAL_baseline[7:9], Comorbid_code)
  #this is hashed out here to make table summing / generation easier for baseline co-morbid states
  #CAL_baseline[10:17]<-lapply(CAL_baseline[10:17], Comorbid_code)
  
  CAL_baseline$`6_Parathyroid_Date`<-as.Date(CAL_baseline$`6_Parathyroid_Date`, "%d/%m/%Y")
  CAL_baseline$`6_Reimplantation`<-NULL #Dropped presently for analysis as no key availalbe to understand coding
  
  #standardise iPTH and PTH units to pmol/L
  CAL_baseline$`7_iPTH`<-ifelse(CAL_baseline$`7_iPTH`>0 & CAL_baseline$`7_iPTH_Unit`=="ng/L", CAL_baseline$`7_iPTH`*0.106, CAL_baseline$`7_iPTH`)
  CAL_baseline$`7_iPTH`<-round(CAL_baseline$`7_iPTH`, digits=0)
  CAL_baseline$`7_iPTH_Unit`<-NULL
  CAL_baseline$`7_PTH`<-ifelse(CAL_baseline$`7_PTH`>0 & CAL_baseline$`7_PTH_Unit`=="ng/L", CAL_baseline$`7_PTH`*0.106, CAL_baseline$`7_PTH`)
  CAL_baseline$`7_PTH`<-round(CAL_baseline$`7_PTH`, digits=0)
  CAL_baseline$`7_PTH_Unit`<-NULL
  
  CAL_baseline$`7_CRP`<-round(CAL_baseline$`7_CRP`, digits=0)
  
  #standardise haemoglobin values to g/dL
  CAL_baseline$`7_Haemoglobin`<-ifelse(CAL_baseline$`7_Haemoglobin`>0 & CAL_baseline$`7_Haemoglobin_Unit`=="g/L" | CAL_baseline$`7_Haemoglobin`>0 & CAL_baseline$`7_Haemoglobin_Unit`=="g/l", CAL_baseline$`7_Haemoglobin`/10, CAL_baseline$`7_Haemoglobin`)
  CAL_baseline$`7_Haemoglobin_Unit`<-NULL
  
  #clean RRT data
  CAL_baseline$`8_Haemodialysis_Sessions`[CAL_baseline$`8_Haemodialysis_Sessions`=="0"]<-NA #remove 0 as integer fornumber of HD sessions - this has been entered for some transplant patients
  CAL_baseline$`8_Haemodialysis_KtV`<-NULL #significant missing data (58/71)
  CAL_baseline$`8_Haemodialysis_BloodUreaReductionRatio`[CAL_baseline$`8_Haemodialysis_BloodUreaReductionRatio`=="N/A"]<-NA #correctly label na values 
  CAL_baseline$`8_Haemodialysis_BloodUreaReductionRatio`<-gsub("%", "", CAL_baseline$`8_Haemodialysis_BloodUreaReductionRatio`)
  CAL_baseline$`8_Haemodialysis_BloodUreaReductionRatio`<-as.numeric(as.character(CAL_baseline$`8_Haemodialysis_BloodUreaReductionRatio`))
  CAL_baseline$`8_Haemodialysis_BloodUreaReductionRatio`<-round(CAL_baseline$`8_Haemodialysis_BloodUreaReductionRatio`, digits=0)
    #remove PD data as only 4 patients hence uninformative for detailed analysis
    CAL_baseline$`8_PeritonealDialysis_KtV`<-NULL
    CAL_baseline$`8_PeritonealDialysis_KtV`<-NULL
    CAL_baseline$`8_PeritonealDialysis_Therapy`<-NULL
    CAL_baseline$`8_PeritonealDialysis_Creatinine`<-NULL
    CAL_baseline$`8_PeritonealDialysis_DialysisVolume`<-NULL
    
  #Vitamin d
  #CAL_baseline[34:35]<-lapply(CAL_baseline[35:35], Comorbid_code)
  CAL_baseline$`9_DrugName`<-ifelse(CAL_baseline$`9_DrugName`=="alfacalcidol" 
                                    |CAL_baseline$`9_DrugName`=="alpha calcidol" 
                                    | CAL_baseline$`9_DrugName`=="alphacacidol" 
                                    | CAL_baseline$`9_DrugName`=="alphacalcidol" 
                                    | CAL_baseline$`9_DrugName`=="one alpha calcidol" 
                                    | CAL_baseline$`9_DrugName`=="onealphacalcidol" 
                                    |CAL_baseline$`9_DrugName`=="Alphacalcidol", "Alphacalcidol", 
                                    ifelse(CAL_baseline$`9_DrugName`=="calcitriol"
                                    | CAL_baseline$`9_DrugName`=="Calcitrol", "Calcitriol", 
                                    ifelse(CAL_baseline$`9_DrugName`=="Colecalciferol"
                                    |CAL_baseline$`9_DrugName`=="Colecalciferol 800", "Colecalciferol", 
                                    ifelse(CAL_baseline$`9_DrugName`=="paricalcitol", "Paricalcitol", NA))))
  CAL_baseline$`9_Dose`<-NULL #inconsistent; needs review before use in analysis
  CAL_baseline$`9_Unit`<-NULL #dependent on above
  CAL_baseline$`9_Frequency`<-NULL #dependent on above
  CAL_baseline$`9_Duration`<-NULL #needs discussion with study leads
  
  #make PO4 binder binary
  # CAL_baseline[37]<-lapply(CAL_baseline[37], Comorbid_code) - hashed out for tabulation
  #huge spread of binder names - simplify to Number of binders / Ca containing binder
  CAL_baseline$`9_PhosphateBinders_DrugName1`<-as.numeric(as.character(CAL_baseline$`9_PhosphateBinders_DrugName1`))
  CAL_baseline$`9_PhosphateBinders_DrugName2`<-as.numeric(as.character(CAL_baseline$`9_PhosphateBinders_DrugName2`))
  CAL_baseline$`9_PhosphateBinders_DrugName3`<-as.numeric(as.character(CAL_baseline$`9_PhosphateBinders_DrugName3`))
    #drop redundent data for analysis
    CAL_baseline$`9_PhosphateBinder_Dose1`<-NULL
    CAL_baseline$`9_PhosphateBinder_Dose2`<-NULL
    CAL_baseline$`9_PhosphateBinder_Dose3`<-NULL
    CAL_baseline$`9_PhosphateBinder_Unit1`<-NULL
    CAL_baseline$`9_PhosphateBinder_Unit2`<-NULL
    CAL_baseline$`9_PhosphateBinder_Unit3`<-NULL
    CAL_baseline$`9_PhosphateBinder_Duration1`<-NULL
    CAL_baseline$`9_PhosphateBinder_Duration2`<-NULL
    CAL_baseline$`9_PhosphateBinder_Duration3`<-NULL
    CAL_baseline$`9_PhosphateBinder_Frequency1`<-NULL
    CAL_baseline$`9_PhosphateBinder_Frequency2`<-NULL
    CAL_baseline$`9_PhosphateBinder_Frequency3`<-NULL
    CAL_baseline$`9_PhosphateBinders_DrugName1_Other`<-NULL
    CAL_baseline$`9_PhosphateBinders_DrugName2_Other`<-NULL
    CAL_baseline$`9_PhosphateBinders_DrugName3_Other`<-NULL
  
    CAL_baseline$`9_Binder_Number`<-ifelse(CAL_baseline$`9_PhosphateBinders_DrugName1`>0 
                                           & CAL_baseline$`9_PhosphateBinders_DrugName2`>0 
                                           & CAL_baseline$`9_PhosphateBinders_DrugName3`>0, 3, 
                                           ifelse(CAL_baseline$`9_PhosphateBinders_DrugName1`>0 
                                           & CAL_baseline$`9_PhosphateBinders_DrugName2`>0 
                                           & CAL_baseline$`9_PhosphateBinders_DrugName3`<0, 2, 
                                           ifelse(CAL_baseline$`9_PhosphateBinders_DrugName1`>0 
                                           & CAL_baseline$`9_PhosphateBinders_DrugName2`<0 
                                           & CAL_baseline$`9_PhosphateBinders_DrugName3`<0, 1, 0)))
    
    CAL_baseline$`9_Phosphate_Binder_Calcium`<-ifelse(CAL_baseline$`9_PhosphateBinders_DrugName1`=="4"
                                                      |CAL_baseline$`9_PhosphateBinders_DrugName1`=="5"
                                                      |CAL_baseline$`9_PhosphateBinders_DrugName1`=="7"
                                                      |CAL_baseline$`9_PhosphateBinders_DrugName1`=="8"
                                                      |CAL_baseline$`9_PhosphateBinders_DrugName2`=="4"
                                                      |CAL_baseline$`9_PhosphateBinders_DrugName2`=="5"
                                                      |CAL_baseline$`9_PhosphateBinders_DrugName2`=="7"
                                                      |CAL_baseline$`9_PhosphateBinders_DrugName2`=="8"
                                                      |CAL_baseline$`9_PhosphateBinders_DrugName3`=="4"
                                                      |CAL_baseline$`9_PhosphateBinders_DrugName3`=="5"
                                                      |CAL_baseline$`9_PhosphateBinders_DrugName3`=="7"
                                                      |CAL_baseline$`9_PhosphateBinders_DrugName3`=="8", "1", "0")
    
    CAL_baseline$`9_Phosphate_Binder_Calcium`<-as.numeric(as.character(CAL_baseline$`9_Phosphate_Binder_Calcium`))
    
    CAL_baseline$`9_PhosphateBinders_DrugName1`<-NULL
    CAL_baseline$`9_PhosphateBinders_DrugName2`<-NULL
    CAL_baseline$`9_PhosphateBinders_DrugName3`<-NULL
    #move these new columns into the appropriate position
    CAL_baseline<-CAL_baseline[,c(1:37,74,75,38:73)]
    #calcimimetics - relabel and drop additional info
    # CAL_baseline[40]<-lapply(CAL_baseline[40], Comorbid_code)
      CAL_baseline$`9_Calcimimetics_DrugName`<-NULL
      CAL_baseline$`9_Calcimimetics_Unit`<-NULL
      CAL_baseline$`9_Calcimimetics_Dose`<-NULL
      CAL_baseline$`9_Calcimimetics_Frequency`<-NULL
      CAL_baseline$`9_Calcimimetics_Duration`<-NULL
   #CAL_baseline[41]<-lapply(CAL_baseline[41], Comorbid_code)
   #CAL_baseline[43:44]<-lapply(CAL_baseline[43:44], Comorbid_code)
   CAL_baseline$`9_Calcimimetics_VitaminK_Indication`<-NULL #almost all for AF
   
   #baseline diagnosis of calciphlaxis details
   CAL_baseline$`10_Date`<-as.Date(CAL_baseline$`10_Date`, "%d/%m/%Y")
   #CAL_baseline[46]<-lapply(CAL_baseline[46], Comorbid_code)
   CAL_baseline$`10_ContributingEvent`<-NULL
   CAL_baseline$`10_ContributingEventIfYes`<-NULL #12 contributing events recorded, 4 trauma, 8 other. Limited use in analysis at present
   #CAL_baseline[46:51]<-lapply(CAL_baseline[46:51], Comorbid_code) #hashed out recode for tablulation purposes
   CAL_baseline$`10_DiagnosisMadeBy_Other`<-NULL #not used at this time
   #CAL_baseline[52:61]<-lapply(CAL_baseline[52:61], Comorbid_code) #hashed out recode for tablulation purposes
   CAL_baseline$`10_LocationOfLesions_Other`<-NULL
   CAL_baseline[62]<-lapply(CAL_baseline[62], Comorbid_code)
   
   #drop final three biochemical columns due to missing data
   CAL_baseline$`10_Phosphate`<-NULL
   CAL_baseline$`10_MaximumSerum`<-NULL
   CAL_baseline$`10_PTH`<-NULL 
 
###########################################################################################################   
     
###NOW CLEAN THE FOLLOW UP DATA SHEET
   CAL_followup$Date<-as.Date(CAL_followup$Date, "%d/%m/%Y")
   CAL_followup$LocalContactEmail<-NULL
   
   #format dates (these are now dropped as minimal difference from actual follow up date)
   CAL_followup$`1_Creatinine_Date`<-as.Date(CAL_followup$`1_Creatinine_Date`, "%d/%m/%Y")
   CAL_followup$`1_Calcium_Date`<-as.Date(CAL_followup$`1_Calcium_Date`, "%d/%m/%Y")
   CAL_followup$`1_CorrectedCalcium_Date`<-as.Date(CAL_followup$`1_CorrectedCalcium_Date`, "%d/%m/%Y")
   CAL_followup$`1_PTH_Date`<-as.Date(CAL_followup$`1_PTH_Date`, "%d/%m/%Y")
   CAL_followup$`1_iPTH_Date`<-as.Date(CAL_followup$`1_iPTH_Date`, "%d/%m/%Y")
   CAL_followup$`1_TotalProtein_Date`<-as.Date(CAL_followup$`1_TotalProtein_Date`, "%d/%m/%Y")
   CAL_followup$`1_Albumin_Date`<-as.Date(CAL_followup$`1_Albumin_Date`, "%d/%m/%Y")
   CAL_followup$`1_AlkalinePhosphatise_Date`<-as.Date(CAL_followup$`1_AlkalinePhosphatise_Date`, "%d/%m/%Y")
   CAL_followup$`1_CRP_Date`<-as.Date(CAL_followup$`1_CRP_Date`, "%d/%m/%Y")
   CAL_followup$`1_Haemoglobin_Date`<-as.Date(CAL_followup$`1_Haemoglobin_Date`, "%d/%m/%Y")
   CAL_followup$`1_Phosphate_Date`<-as.Date(CAL_followup$`1_Phosphate_Date`, "%d/%m/%Y")
   
     CAL_followup$`1_Creatinine_Date`<-NULL
     CAL_followup$`1_Calcium_Date`<-NULL
     CAL_followup$`1_CorrectedCalcium_Date`<-NULL
     CAL_followup$`1_PTH_Date`<-NULL
     CAL_followup$`1_iPTH_Date`<-NULL
     CAL_followup$`1_TotalProtein_Date`<-NULL
     CAL_followup$`1_Albumin_Date`<-NULL
     CAL_followup$`1_AlkalinePhosphatise_Date`<-NULL
     CAL_followup$`1_CRP_Date`<-NULL
     CAL_followup$`1_Haemoglobin_Date`<-NULL
     CAL_followup$`1_Phosphate_Date`<-NULL
     
    CAL_followup$`2_LocationOfLesions_Other`<-NULL
    CAL_followup$`3_MedicalInterventions_DialysisModalityDescribe`<-NULL
    CAL_followup$`3_MedicalInterventionsBisphosphonates_Name`<-NULL
    CAL_followup$`3_MedicalInterventionsBisphosphonates_Dose`<-NULL
    CAL_followup$`3_MedicalInterventionsBisphosphonates_Route`<-NULL
    CAL_followup$`3_MedicalInterventiosnBisphosphonates_Length`<-NULL
    CAL_followup$`3_MedicalInterventionsHyperbaricOxygen_Prescription`<-NULL
    CAL_followup$`3_MedicalInterventiosnSodiumThiosulphate_Length`<-NULL
    CAL_followup$`3_MedicalInterventionsSodiumThiosulphate_Dose`<-NULL
    
    CAL_followup[15:41]<-lapply(CAL_followup[15:41], Comorbid_code)
    
    CAL_followup$`4_ParathyroidectomyDate`<-as.Date(CAL_followup$`4_ParathyroidectomyDate`, "%d/%m/%Y")
    
    CAL_followup$`4_Other`<-NULL
    
    CAL_followup[43:59]<-lapply(CAL_followup[43:59], Comorbid_code)
    
    CAL_followup$`7_SkinLesionsResolveDate`<-as.Date(CAL_followup$`7_SkinLesionsResolveDate`, "%d/%m/%Y")
    
    #end points - clean up death information
    CAL_followup$`8_Death`[CAL_followup$`8_Death`=="N/A"]<-NA #remove 0 as integer fornumber of HD sessions - this has been entered for some transplant patients
    CAL_followup$`8_Death`[CAL_followup$`8_Death`=="N/A pt still alive"]<-NA #remove 0 as integer fornumber of HD sessions - this has been entered for some transplant patients
    CAL_followup$`8_Death`[CAL_followup$`8_Death`=="unknown"]<-NA #remove 0 as integer fornumber of HD sessions - this has been entered for some transplant patients
    CAL_followup$`8_Death`<-ifelse(is.na(CAL_followup$`8_Death`), 0,1)
    
      #placeholder update as ID 84 is RIP and not properly recorded in provided data
      CAL_followup$`8_Death`<-ifelse(CAL_followup$StudyID=="84",1,CAL_followup$`8_Death`)
    
    CAL_followup[62:63]<-lapply(CAL_followup[62:63], Comorbid_code)
    
    CAL_followup$`11_Comments`<-NULL 
```

```{r echo=FALSE}

#TIME STAMPS
    Date_report<-Sys.Date()
    Date_report<-format(Date_report, '%d %B, %Y')
```

This is a summary report for the calciphylaxis data prior to ERA-EDTA.  This  analysis was run on `r Date_report`.  

# Summary of baseline data

```{r echo=FALSE}
#CODE FOR DESCRIPTIVE DEMOGRAPHIC DATA
   
    #demographics
    Gender_completeness<- (nrow(CAL_baseline)-sum(is.na(CAL_baseline$`1b_Gender`)))
    Male_no<- sum(CAL_baseline$`1b_Gender`=="Male", na.rm=T)
    Female_no<- sum(CAL_baseline$`1b_Gender`=="Female", na.rm=T)
    
    Age_dist<-shapiro.test(CAL_baseline$`1c_Age`)
    Age_dist<-round(Age_dist$p.value, digits=2)
    
    Age_missing<-sum(is.na(CAL_baseline$`1c_Age`))
    
    Age_overall_mean<- round(mean(CAL_baseline$`1c_Age`, na.rm=T), digits=1)
    Age_overall_SD<-round(mean(CAL_baseline$`1c_Age`, na.rm=T), digits=1)
    
    Male<-subset(CAL_baseline, CAL_baseline$`1b_Gender`=="Male")
    Male_mean<-round(mean(Male$`1c_Age`, na.rm=T), digits=1)
    
    Female<-subset(CAL_baseline, CAL_baseline$`1b_Gender`=="Female")
    Female_mean<-round(mean(Female$`1c_Age`, na.rm=T), digits=1)
    
    Age.t<-t.test(CAL_baseline$`1c_Age`~CAL_baseline$`1b_Gender`)
    Age.t.p<-round(Age.t$p.value, digits=2)
    
      Caucasian<-subset(CAL_baseline_unedited, CAL_baseline_unedited$`2_Race`=="1")
      Non_caucasian<-(nrow(CAL_baseline) - nrow(Caucasian))
      CAL_baseline_unedited$`2_Race`[CAL_baseline_unedited$`2_Race`=="-1"] <-NA
      Ethnicity_missing<-sum(is.na(CAL_baseline_unedited$`2_Race`))
      weight_missing<-sum(is.na(CAL_baseline_unedited$`1d_Weight`))
      bmi_missing<-sum(is.na(CAL_baseline_unedited$`1e_BMI`))
    #consent dates
    Consent_first<-format(min(CAL_baseline$`1a_ConsentDate`), '%d %B, %Y')
    Consent_last<-format(max(CAL_baseline$`1a_ConsentDate`), '%d %B, %Y')
    
    #diagnosis data
    No_diag_date<-sum(is.na(CAL_baseline$`10_Date`))
    Diagnosis_known<-nrow(CAL_baseline)-No_diag_date
    
    Diag_min<-min(CAL_baseline$`10_TimeFromOnset`, na.rm=T)
    Diag_max<-max(CAL_baseline$`10_TimeFromOnset`, na.rm=T)
    
```

This analysis includes `r nrow(CAL_baseline)` baseline records for patients recruited between `r Consent_first` and `r Consent_last`.  

##Demographics

Gender data were available for `r Gender_completeness` patients. Of these, `r Male_no` (`r round(100*(Male_no)/Gender_completeness, digits=1)`%) were male and `r Female_no` (`r round(100*(Female_no)/Gender_completeness, digits=1)`%) were female.  

The distribution of age data approximated normality (Shapiro test p=`r Age_dist`).  Mean age was `r Age_overall_mean` ± `r Age_overall_SD` years (`r Male_mean` males, `r Female_mean` females, p = `r Age.t.p`). Age data were missing for `r Age_missing` patients.

Ethnicity is not considered in this analysis as only `r Non_caucasian` patients are coded as non-Caucasian (of whom `r Ethnicity_missing` have missing data.
Weight and BMI data are not described due to limited information being present (weight data missing in `r weight_missing`; BMI data missing in `r bmi_missing`).

Date of diagnosis of calciphlaxis is documented for `r Diagnosis_known` patients. Time from diagnosis to consent ranges from `r Diag_min` to `r Diag_max` days.
\newpage

## Renal status

```{r echo=FALSE}
#CODE FOR DESCRIPTIVE ORGAN SUPPORT DATA
    
  renal_status<-nrow(CAL_baseline) - sum(is.na(CAL_baseline$`4_RenalStatus`))
  renal_status_pct<-round(100*(renal_status/nrow(CAL_baseline)), digits=1)
  
  renal_earliest<-min(CAL_baseline$`3_DateFirstTreatment`, na.rm=TRUE)
  renal_earliest<-format(renal_earliest, '%d %B, %Y')
  
  renal_latest<-max(CAL_baseline$`3_DateFirstTreatment`, na.rm=TRUE)
  renal_latest<-format(renal_latest, '%d %B, %Y')
  
  CAL_baseline$renal_time<-CAL_baseline$`1a_ConsentDate`-CAL_baseline$`3_DateFirstTreatment`
  CAL_baseline$renal_time<-as.numeric(CAL_baseline$renal_time)
    median_renal_time<-round(median(CAL_baseline$renal_time, na.rm=T), digits=0)
    min_renal_time<-min(CAL_baseline$renal_time, na.rm=T)
    max_ren_time<-as.numeric(max(CAL_baseline$renal_time, na.rm=T))
    #this next line is needed to avoid e.g. 4*10{4} notation
    max_ren_time<-format(max_ren_time,scientific=FALSE)
  
  #NEED TABLE ON MODALITIES  
    modality_table<-table(CAL_baseline$`4_RenalStatus`)
    
  #previous modality information
    #transplant
  tx_prev_rrt<-ifelse(CAL_baseline$`4_RenalStatus`=="Transplant"  & CAL_baseline$`5_PreviousRR_PD`=="Yes" |CAL_baseline$`4_RenalStatus`=="Transplant"  & CAL_baseline$`5_PreviousRR_HDHDF`=="Yes", 1,0)  
```

Data on renal background were availabe for `r renal_status` patients (`r renal_status_pct`%). The earliest documented occurance of or organ support was `r renal_earliest` with the most recent occuring at `r renal_latest`. 

The median time between ESRD / organ support and consent to the study was `r median_renal_time` days (range `r min_renal_time` to `r max_ren_time` days).

Most patients with a documented renal status were on haemodialysis / haemodiafiltration :

Renal status | Number
-------------|---------
`r names(modality_table[1])`|`r modality_table[1]`
`r names(modality_table[2])`|`r modality_table[2]`
`r names(modality_table[3])`|`r modality_table[3]`
`r names(modality_table[4])`|`r modality_table[4]`
`r names(modality_table[5])`|`r modality_table[5]`
`r names(modality_table[6])`|`r modality_table[6]`

Of the `r modality_table[6]` patients with a `r names(modality_table[6])`, `r sum(tx_prev_rrt, na.rm=T)` had a history of either haemodialysis / haemodiafiltration or peritoneal dialysis.

```{r echo=FALSE}
### out of order - do section 8 to describe HD time / cCa in fluid 
  
  CAL_baseline_HD<-subset(CAL_baseline, CAL_baseline$`4_RenalStatus`=="HD/HDF")
  
  #missing HD data 
  HD_missing<-sum(is.na(CAL_baseline_HD$`8_Haemodialysis_Sessions`))
  
  CAL_baseline_HD$`8_Haemodialysis_Sessions`<-as.factor(as.character(CAL_baseline_HD$`8_Haemodialysis_Sessions`))
  CAL_baseline_HD$`8_Haemodialysis_Minutes`<-as.factor(as.character(CAL_baseline_HD$`8_Haemodialysis_Minutes`))
  
  HD_mins<-levels(CAL_baseline_HD$`8_Haemodialysis_Minutes`)
  HD_sessions<-levels(CAL_baseline_HD$`8_Haemodialysis_Sessions`)

  jim<-table(CAL_baseline_HD$`8_Haemodialysis_Sessions`, CAL_baseline_HD$`8_Haemodialysis_Minutes`)
  
  Cal_min<-min(CAL_baseline_HD$`8_Haemodialysis_DialysateCalciumConcentration`, na.rm=T)
  Cal_max<-max(CAL_baseline_HD$`8_Haemodialysis_DialysateCalciumConcentration`, na.rm=T)
  Cal_med<-median(CAL_baseline_HD$`8_Haemodialysis_DialysateCalciumConcentration`, na.rm=T)
  
  Cal_med<-median(CAL_baseline_HD$`8_Haemodialysis_DialysateCalciumConcentration`, na.rm=T)
  Cal_q25 <-quantile(CAL_baseline_HD$`8_Haemodialysis_DialysateCalciumConcentration`, 0.25, na.rm=T )
  Cal_q75 <-quantile(CAL_baseline_HD$`8_Haemodialysis_DialysateCalciumConcentration`, 0.75, na.rm=T )
```


Of the `r modality_table[4]` patients on haemodialysis or haemodiafiltration, data on dialysis sessions / hours were missing for `r HD_missing` patients.
At the time of consent, most patients were on a standard prescription for time on dialysis:

Mins / sessions| 2|3|4|5|6|7
-----|-|-|-|-|-|-
`r names(jim[1,][1])` |`r jim[1,1]` |`r jim[2,1]` |`r jim[3,1]` |`r jim[4,1]` |`r jim[5,1]` |`r jim[6,1]`
`r names(jim[1,][2])` |`r jim[1,2]` |`r jim[2,2]` |`r jim[3,2]` |`r jim[4,2]` |`r jim[5,2]` |`r jim[6,2]`
`r names(jim[1,][3])` |`r jim[1,3]` |`r jim[2,3]` |`r jim[3,3]` |`r jim[4,3]` |`r jim[5,3]` |`r jim[6,3]`
`r names(jim[1,][4])` |`r jim[1,4]` |`r jim[2,4]` |`r jim[3,4]` |`r jim[4,4]` |`r jim[5,4]` |`r jim[6,4]`
`r names(jim[1,][5])` |`r jim[1,5]` |`r jim[2,5]` |`r jim[3,5]` |`r jim[4,5]` |`r jim[5,5]` |`r jim[6,5]`
`r names(jim[1,][6])` |`r jim[1,6]` |`r jim[2,6]` |`r jim[3,6]` |`r jim[4,6]` |`r jim[5,6]` |`r jim[6,6]`

Dialysate calcium concentrations ranged from `r Cal_min` to `r Cal_max` mmol/L, with a median value of `r Cal_med` mmol/L (IQR `r Cal_q25` - `r Cal_q75`).


\newpage

## Baseline co-morbidity

```{r, echo=FALSE}

  #unlike the cleaned data (prepared for easy reading, comorbid codes have been left as 1/0)
  #therefore need to reassign -1 to NA
  Calciphylaxis_NA_remove<- function(x) {
                     
    x[x=="-1"]<-NA
    x<<-as.numeric(as.character(x))
  }
  
  CAL_baseline[10:17]<-lapply(CAL_baseline[10:17], Calciphylaxis_NA_remove)
  
  #sinlge line of code to address the fact that 'Heart disease' has a single field coded as "3"
  CAL_baseline$`6_HeartDisease`[CAL_baseline$`6_HeartDisease`=="3"]<-NA
  
  #replace 2 with 0 for negative responses
  Calciphylaxis_two_remove<- function(x) {
                     
    x[x=="2"]<-0
    x<<-as.numeric(as.character(x))
  }
  CAL_baseline[10:17]<-lapply(CAL_baseline[10:17], Calciphylaxis_two_remove)
  
  #count na values for comorbidities
  com_na_count <-sapply(CAL_baseline[10:17], function(y) sum(length(which(is.na(y)))))
  
  #count numbers of patients with a comorbidity
  com_count <-sapply(CAL_baseline[10:17], function(y) sum(y, na.rm=T ))
  
  #tidy name values
  names(com_na_count)<-sapply(names(com_na_count), function(y) gsub("6_", "",(y)))
  
  #percentage values - those with data
  com_pct <- round  (100*(com_count/(nrow(CAL_baseline) - com_na_count)), digits=1)
  
  #percentage values - all patients
  com_pct_all <- round  (100*(com_count/nrow(CAL_baseline)), digits=1)
  
```

Comorbidity | n= missing data | n = present | Percentage with data| Percentage of all patients
------------|------------|-------------|------------|----
`r names(com_na_count[1])`|`r com_na_count[1]`| `r com_count[1]`  |  `r com_pct[1]`|`r com_pct_all[1]`
`r names(com_na_count[2])`|`r com_na_count[2]`| `r com_count[2]`  |  `r com_pct[2]`|`r com_pct_all[2]`
`r names(com_na_count[3])`|`r com_na_count[3]`| `r com_count[3]`  |  `r com_pct[3]`|`r com_pct_all[3]`
`r names(com_na_count[4])`|`r com_na_count[4]`| `r com_count[4]`  |  `r com_pct[4]`|`r com_pct_all[4]`
`r names(com_na_count[5])`|`r com_na_count[5]`| `r com_count[5]`  |  `r com_pct[5]`|`r com_pct_all[5]`
`r names(com_na_count[6])`|`r com_na_count[6]`| `r com_count[6]`  |  `r com_pct[6]`|`r com_pct_all[6]`
`r names(com_na_count[7])`|`r com_na_count[7]`| `r com_count[7]`  |  `r com_pct[7]`|`r com_pct_all[7]`
`r names(com_na_count[8])`|`r com_na_count[8]`| `r com_count[8]`  |  `r com_pct[8]`|`r com_pct_all[8]`


```{r echo=FALSE}
 #data for biochemistry table
  
    biochem_na_count <-sapply(CAL_baseline[19:28], function(y) sum(length(which(is.na(y)))))
  
    biochem_mean <-sapply(CAL_baseline[19:28], function(y) mean(y, na.rm=T ))
    biochem_mean<-round(biochem_mean, digits=1)
    
    biochem_sd <-sapply(CAL_baseline[19:28], function(y) sd(y, na.rm=T ))
    biochem_sd<-round(biochem_sd, digits=1)
    
    biochem_median<-sapply(CAL_baseline[19:28], function(y) median(y, na.rm=T ))
    biochem_median<-round(biochem_median, digits=1)
    
    biochem_q25 <-sapply(CAL_baseline[19:28], function(y) quantile(y,c(.25), na.rm=T ))
    biochem_25<-round(biochem_q25, digits=1)
    
    biochem_q75 <-sapply(CAL_baseline[19:28], function(y) quantile(y, c(.75), na.rm=T ))
    biochem_75<-round(biochem_q75, digits=1)
    
    names(biochem_na_count)<-sapply(names(biochem_na_count), function(y) gsub("7_", "",(y)))

```
Biochemistry | n= missing data | Mean | SD | Median | 25th | 75th
-------------|-----------------|----- |----|--------|------|------
`r names(biochem_na_count[1])`|`r biochem_na_count[1]`| `r biochem_mean[1]`  |  `r biochem_sd[1]` | `r biochem_median[1]` | `r biochem_q25[1]` | `r biochem_q75[1]` 
`r names(biochem_na_count[2])`|`r biochem_na_count[2]`| `r biochem_mean[2]`  |  `r biochem_sd[2]` | `r biochem_median[2]` | `r biochem_q25[2]` | `r biochem_q75[2]` 
`r names(biochem_na_count[3])`|`r biochem_na_count[3]`| `r biochem_mean[3]`  |  `r biochem_sd[3]` | `r biochem_median[3]` | `r biochem_q25[3]` | `r biochem_q75[3]` 
`r names(biochem_na_count[4])`|`r biochem_na_count[4]`| `r biochem_mean[4]`  |  `r biochem_sd[4]` | `r biochem_median[4]` | `r biochem_q25[4]` | `r biochem_q75[4]` 
`r names(biochem_na_count[5])`|`r biochem_na_count[5]`| `r biochem_mean[5]`  |  `r biochem_sd[5]` | `r biochem_median[5]` | `r biochem_q25[5]` | `r biochem_q75[5]` 
`r names(biochem_na_count[6])`|`r biochem_na_count[6]`| `r biochem_mean[6]`  |  `r biochem_sd[6]` | `r biochem_median[6]` | `r biochem_q25[6]` | `r biochem_q75[6]` 
`r names(biochem_na_count[7])`|`r biochem_na_count[7]`| `r biochem_mean[7]`  |  `r biochem_sd[7]` | `r biochem_median[7]` | `r biochem_q25[7]` | `r biochem_q75[7]` 
`r names(biochem_na_count[8])`|`r biochem_na_count[8]`| `r biochem_mean[8]`  |  `r biochem_sd[8]` | `r biochem_median[8]` | `r biochem_q25[8]` | `r biochem_q75[8]` 
`r names(biochem_na_count[9])`|`r biochem_na_count[9]`| `r biochem_mean[9]`  |  `r biochem_sd[9]` | `r biochem_median[9]` | `r biochem_q25[9]` | `r biochem_q75[9]` 
`r names(biochem_na_count[10])`|`r biochem_na_count[10]`| `r biochem_mean[10]`  |  `r biochem_sd[10]` | `r biochem_median[10]` | `r biochem_q25[10]` | `r biochem_q75[10]` 

\newpage

## Contributory factors
```{r echo=FALSE}

    ###Need to address section 9 - first remove -1 and recode 2 values
    
    CAL_baseline[34:35]<-lapply(CAL_baseline[34:35], Calciphylaxis_NA_remove)
    CAL_baseline[34:35]<-lapply(CAL_baseline[34:35], Calciphylaxis_two_remove)
    
    
    CAL_baseline[37]<-lapply(CAL_baseline[37], Calciphylaxis_NA_remove)
    CAL_baseline[37]<-lapply(CAL_baseline[37], Calciphylaxis_two_remove)
    
    CAL_baseline[40:43]<-lapply(CAL_baseline[40:43], Calciphylaxis_NA_remove)
    CAL_baseline[40:43]<-lapply(CAL_baseline[40:43], Calciphylaxis_two_remove)
    
    #as columns are separated, create subset df for these to be done easily (note iv route discared here)
    Section_9 <- CAL_baseline[c(1,34,37,40:43)]
    
    #count na values for comorbidities
  ppt_na_count <-sapply(Section_9[2:7], function(y) sum(length(which(is.na(y)))))
  
  #count numbers of patients with a comorbidity
  ppt_count <-sapply(Section_9[2:7], function(y) sum(y, na.rm=T ))
  
  #tidy name values
  names(ppt_na_count)<-sapply(names(ppt_na_count), function(y) gsub("9_", "",(y)))
  
  #percentage values - those with data
  ppt_pct <- round  (100*(ppt_count/(nrow(Section_9) - ppt_na_count)), digits=1)
  
  #percentage values - those with data
  #com_pct <- round  (100*(com_count/(nrow(CAL_baseline) - com_na_count)), digits=1)
  
  #percentage values - all patients
  ppt_pct_all <- round  (100*(ppt_count/nrow(Section_9)), digits=1)
  
  #count patients on a PO4 binder containing calcium
  Ca_binder<-sum(CAL_baseline$`9_Phosphate_Binder_Calcium`)
    
```

Risk factor | n= missing data | n = present | Percentage with data| Percentage of all patients
------------|------------|-------------|------------|----
`r names(ppt_na_count[1])`|`r ppt_na_count[1]`| `r ppt_count[1]`  |  `r ppt_pct[1]`|`r ppt_pct_all[1]`
`r names(ppt_na_count[2])`|`r ppt_na_count[2]`| `r ppt_count[2]`  |  `r ppt_pct[2]`|`r ppt_pct_all[2]`
`r names(ppt_na_count[3])`|`r ppt_na_count[3]`| `r ppt_count[3]`  |  `r ppt_pct[3]`|`r ppt_pct_all[3]`
`r names(ppt_na_count[4])`|`r ppt_na_count[4]`| `r ppt_count[4]`  |  `r ppt_pct[4]`|`r ppt_pct_all[4]`
`r names(ppt_na_count[5])`|`r ppt_na_count[5]`| `r ppt_count[5]`  |  `r ppt_pct[5]`|`r ppt_pct_all[5]`
`r names(ppt_na_count[6])`|`r ppt_na_count[6]`| `r ppt_count[6]`  |  `r ppt_pct[6]`|`r ppt_pct_all[6]`
`r names(ppt_na_count[7])`|`r ppt_na_count[7]`| `r ppt_count[7]`  |  `r ppt_pct[7]`|`r ppt_pct_all[7]`

Of the `r ppt_count[2]` patients prescribed a phosphate binder, `r Ca_binder` were prescribed a calcium containing drug.


\newpage
```{r echo=FALSE}
#diagnosis columns have been left as numeric - need to address as above:
    CAL_baseline[46:51]<-lapply(CAL_baseline[46:51], Calciphylaxis_NA_remove)
    CAL_baseline[46:51]<-lapply(CAL_baseline[46:51], Calciphylaxis_two_remove)

    #46 - 51 are diagnosis codes
    
     #count na values for comorbidities
  diag_na_count <-sapply(CAL_baseline[46:51], function(y) sum(length(which(is.na(y)))))
  
  #count numbers of patients with a comorbidity
  diag_count <-sapply(CAL_baseline[46:51], function(y) sum(y, na.rm=T ))
  
  #tidy name values
  names(diag_na_count)<-sapply(names(diag_na_count), function(y) gsub("10_DiagnosisMadeBy_", "",(y)))
  
  #percentage values - those with data
  diag_pct <- round  (100*(diag_count/(nrow(CAL_baseline) - diag_na_count)), digits=1)
  
  #percentage values - all recruited
  diag_pct_all <- round  (100*(diag_count/nrow(CAL_baseline)), digits=1)
  
```
## Method of diagnosis
The diagnosis of calciphlyaxis was made as below:

Mode of diagnosis | n= missing data | n = diagnosed this way | Percentage with data | Percentage of all patients
------------|------------|-------------|------------|----
`r names(diag_na_count[1])`|`r diag_na_count[1]`| `r diag_count[1]`  |  `r diag_pct[1]`|  `r diag_pct_all[1]`
`r names(diag_na_count[2])`|`r diag_na_count[2]`| `r diag_count[2]`  |  `r diag_pct[2]`|`r diag_pct_all[2]`
`r names(diag_na_count[3])`|`r diag_na_count[3]`| `r diag_count[3]`  |  `r diag_pct[3]`|`r diag_pct_all[3]`
`r names(diag_na_count[4])`|`r diag_na_count[4]`| `r diag_count[4]`  |  `r diag_pct[4]`|`r diag_pct_all[4]`
`r names(diag_na_count[5])`|`r diag_na_count[5]`| `r diag_count[5]`  |  `r diag_pct[5]`|`r diag_pct_all[5]`
`r names(diag_na_count[6])`|`r diag_na_count[6]`| `r diag_count[6]`  |  `r diag_pct[6]`|`r diag_pct_all[6]`

```{r echo=FALSE}

  #work out how many patients had jsut a clinical diagnosis
  Clinical_diag<-subset(CAL_baseline, CAL_baseline$`10_DiagnosisMadeBy_ClinicaIimpression`=="1")
  Clinical_diag$dual<-ifelse(Clinical_diag$`10_DiagnosisMadeBy_Wound`=="1"|Clinical_diag$`10_DiagnosisMadeBy_SkinBiopsy`=="1",1,0)
  Clincial_dual<-sum(Clinical_diag$dual)
  Clincial_dual_pct<-round(100*(Clincial_dual/nrow(Clinical_diag)), digits=1)
```
Of the `r diag_count[1]` patients with a clinical diagnosis, `r Clincial_dual` (`r Clincial_dual_pct`%) had this diagnosis confirmed by either wound or skin biopsy.

The location of lesions was:

```{r echo=FALSE}
#52:61
  
  #diagnosis columns have been left as numeric - need to address as above:
    CAL_baseline[52:61]<-lapply(CAL_baseline[52:61], Calciphylaxis_NA_remove)
    CAL_baseline[52:61]<-lapply(CAL_baseline[52:61], Calciphylaxis_two_remove)

    #46 - 51 are diagnosis codes
    
     #count na values for comorbidities
  site_na_count <-sapply(CAL_baseline[52:61], function(y) sum(length(which(is.na(y)))))
  
  #count numbers of patients with a comorbidity
  site_count <-sapply(CAL_baseline[52:61], function(y) sum(y, na.rm=T ))
  
  #tidy name values
  names(site_na_count)<-sapply(names(site_na_count), function(y) gsub("10_LocationOfLesions_", "",(y)))
  
  #percentage values - those with data
  site_pct <- round  (100*(site_count/(nrow(CAL_baseline) - site_na_count)), digits=1)
  
  #percentage values - all recruited
  site_pct_all <- round  (100*(site_count/nrow(CAL_baseline)), digits=1)
  
```

Mode of diagnosis | n= missing data | n = diagnosed this way | Percentage with data | Percentage of all patients
------------|------------|-------------|------------|----
`r names(site_na_count[1])`|`r site_na_count[1]`| `r site_count[1]`  |  `r site_pct[1]`|  `r site_pct_all[1]`
`r names(site_na_count[2])`|`r site_na_count[2]`| `r site_count[2]`  |  `r site_pct[2]`|  `r site_pct_all[2]`
`r names(site_na_count[3])`|`r site_na_count[3]`| `r site_count[3]`  |  `r site_pct[3]`|  `r site_pct_all[3]`
`r names(site_na_count[4])`|`r site_na_count[4]`| `r site_count[4]`  |  `r site_pct[4]`|  `r site_pct_all[4]`
`r names(site_na_count[5])`|`r site_na_count[5]`| `r site_count[5]`  |  `r site_pct[5]`|  `r site_pct_all[5]`
`r names(site_na_count[6])`|`r site_na_count[6]`| `r site_count[6]`  |  `r site_pct[6]`|  `r site_pct_all[6]`
`r names(site_na_count[7])`|`r site_na_count[7]`| `r site_count[7]`  |  `r site_pct[7]`|  `r site_pct_all[7]`
`r names(site_na_count[8])`|`r site_na_count[8]`| `r site_count[8]`  |  `r site_pct[8]`|  `r site_pct_all[8]`
`r names(site_na_count[9])`|`r site_na_count[9]`| `r site_count[9]`  |  `r site_pct[9]`|  `r site_pct_all[9]`
`r names(site_na_count[10])`|`r site_na_count[10]`| `r site_count[10]`  |  `r site_pct[10]`|  `r site_pct_all[10]`

```{r echo=FALSE}
#describe the numbers of patients with single / multiple lesion sites
  CAL_baseline$Lesion_number<-rowSums(CAL_baseline[,52:61])
  Lesions_number<-table(CAL_baseline$Lesion_number)
```

The majority of patients had a single lesion:

1 lesion|2 lesions|3 lesions
--------|---------|-----
`r Lesions_number[1]`|`r Lesions_number[2]`|`r Lesions_number[3]`

\newpage

# Follow up data

Several issues need thinking about

1 - time data are available for lesion resolution (subjective), but not for death. This will limit survival analyses

2 - later analyses need to account for the fact that death is a competing risk for lesion resolution

3 - how is lesion resolution defined? e.g. patent 6 has two lesions at baseline. One seems to have resolved at the first follow up point and the second at the second follow up point.  The coding for these follow up visits is non-resolution / resolution respectively.The assumption based on this is that only full resolution should be coded. This may impact senstivity.

4 - for follow up visits, should we use LOCF. eg patient 15 is coded as having binders changed as an intervention at their first follow up. However, at the second follow up this field is coded as a negative. One interpretation is that they went back to their original binder regime.  

5 - data cleaning for follow input. eg patient 15 has 2 follow up datasets with the same date of entry. Presume data entry error as patient died

6 - data cleaning / validation required.  Patient 7 has parathyroid surgery coded as an intervention but these are the same data as in the baseline table.  Will need to review interventions to ensure they are appropriately coded.

7 - needs discussion with trial nurses regarding date values for follow up visits. eg patient 48 has 8 follow up visits but the date values are non-sequential. Is this a data capture issue or are the date values correct and the follow up data need re-ordering?

\newpage

##Association of baseline characteristics with mortality

```{r echo=FALSE}

#First select mortality data
  CAL_Death<-CAL_followup[c("StudyID", "8_Death")]
  #reorder columns so that death coding occurs first for patients with multiple follow up events
  CAL_Death<-CAL_Death[order(CAL_Death$StudyID, -CAL_Death$`8_Death`),]
  #collapse to only a single data point
  CAL_Death<-CAL_Death[!duplicated(CAL_Death$StudyID),]
  
#Now subset baseline exploratory varaibles of interest - ##THIS NEEDS DISCUSSION WITH SMEETA
  CAL_Death_Baseline<-CAL_baseline[c("StudyID", "1c_Age","1b_Gender","4_RenalStatus", "7_Calcium", "7_Haemoglobin", "9_Phosphate_Binder_Calcium", "Lesion_number", "9_Calcimimetics_ACEARBs", "9_Calcimimetics_VitaminK", "9_Calcimimetics_Erythropoetins")]
  
  #Link to form a single dataframe
  CAL_Death_Analysis<-left_join(CAL_Death_Baseline, CAL_Death, by="StudyID")
  
  #subset to select complete cases
  CAL_Death_Analysis<-CAL_Death_Analysis[complete.cases(CAL_Death_Analysis), ] 
  
  #recode and clean
  #assume that calcium values of e.g. 210 have simply misplaced a decimal point
  CAL_Death_Analysis$`7_Calcium`<-ifelse(CAL_Death_Analysis$`7_Calcium`>100, CAL_Death_Analysis$`7_Calcium`/100, CAL_Death_Analysis$`7_Calcium`)
  #similar for haemoglobin (need to be done for inappropraite units both ways)
  CAL_Death_Analysis$`7_Haemoglobin`<-ifelse(CAL_Death_Analysis$`7_Haemoglobin`>20, CAL_Death_Analysis$`7_Haemoglobin`/10, CAL_Death_Analysis$`7_Haemoglobin`)
  CAL_Death_Analysis$`7_Haemoglobin`<-ifelse(CAL_Death_Analysis$`7_Haemoglobin`<1, CAL_Death_Analysis$`7_Haemoglobin`*10, CAL_Death_Analysis$`7_Haemoglobin`)
  #ensure factorial variables correctly coded
   #calcium containing binder
  CAL_Death_Analysis$`9_Phosphate_Binder_Calcium`<-as.factor(CAL_Death_Analysis$`9_Phosphate_Binder_Calcium`)
    #Lesion number.  Make lesion number 1 or greater than 1 due to small numbers of patients with 2 or 3 lesions
  CAL_Death_Analysis$Lesion_number<-ifelse(CAL_Death_Analysis$Lesion_number>1,2,1)
  CAL_Death_Analysis$Lesion_number<-as.factor(CAL_Death_Analysis$Lesion_number)
   #Calcimimetics
  CAL_Death_Analysis$`9_Calcimimetics_ACEARBs`<-as.factor(CAL_Death_Analysis$`9_Calcimimetics_ACEARBs`)
  CAL_Death_Analysis$`9_Calcimimetics_VitaminK`<-as.factor(CAL_Death_Analysis$`9_Calcimimetics_VitaminK`)
  CAL_Death_Analysis$`9_Calcimimetics_Erythropoetins`<-as.factor(CAL_Death_Analysis$`9_Calcimimetics_Erythropoetins`)
   #simplify renal status
  CAL_Death_Analysis$`4_RenalStatus`<-ifelse(CAL_Death_Analysis$`4_RenalStatus`=="CKD5", "CKD", "Organ support")
```

Baseline crosssectional analysis on survival was performed on `r nrow(CAL_Death_Analysis)` patients who had complete baseline data and documented survival status.
 
